---
title: "analysisInfantMortality"
author: "Rachel Griffard"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries
```{r library}
library(mice)
library(VIM)
library(naniar)
library(QuantPsyc)
library(psych)
library(tidyverse)
library(Hmisc)
```

Import full data frames
```{r Import Full Datasets}
IM<-readr::read_csv("../data/Infant_Mortality.csv")
stzIM<-readr::read_csv("../data/stzInfant_Mortality.csv")
```

```{r Correlation}
IMdf <- as.data.frame(IM)
as.integer(IMdf$AverageAlcoholConsumption)
as.integer(IMdf$Mortality)
as.integer(IMdf$AverageAgeofMotherBirth)
as.integer(IMdf$AvgCigaretteSmoking)
as.integer(IMdf$CountryGDPSpentonHealthcare)
as.integer(IMdf$HealthcareLegislation)
as.integer(IMdf$AccesstoANYContraceptiveMethod)
as.integer(IMdf$HighTemperaturebyCountry)
as.integer(IMdf$NegAbort)
as.integer(IMdf$PosAbort)
y <- IMdf[3:11]
x<-IMdf$Mortality

cor(x, y, use="pairwise.complete.obs")

y <- IMdf[2:11]
x<-IMdf$HealthcareLegislation

cor(x, y, use="pairwise.complete.obs")

as.factor(IM$NegAbort)
```





Imputation Testing
```{r Imputation Testing}
sum(is.na(IM))
mean(is.na(IM))
colMeans(is.na(IM))
```

14% missing data
Highest missing data column is 75%, imputations ~75 times to account
|  -Figure out how to do imputations is amount missing data, would rather do highest amount of missing data for average age of mother

Testing for randomness
```{r Randomness}
md.pattern(IM)
aggr(IM, prop = T, numbers = T)
vis_miss(IM)
```
Data is missing completely at Random(MCAR) based on the visual and summary analysess above.

Imputation
```{r Imputation}
imp <- mice(IM, m=75)
```



Model Creation
```{r Model Creation}
fit1 <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking))
fit2 <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking + AccesstoANYContraceptiveMethod))
fit3 <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking + AccesstoANYContraceptiveMethod + CountryGDPSpentonHealthcare))
fit4 <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking + AccesstoANYContraceptiveMethod + CountryGDPSpentonHealthcare + HealthcareLegislation))
fit5p <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking + AccesstoANYContraceptiveMethod + CountryGDPSpentonHealthcare + HealthcareLegislation + ReprodAct + Guideline + EML))
fit5n <- with(imp, lm(Mortality ~ AverageAlcoholConsumption + AverageAgeofMotherBirth + AvgCigaretteSmoking + AccesstoANYContraceptiveMethod + CountryGDPSpentonHealthcare + HealthcareLegislation + PenalCode))

pool1 <- pool(fit1)
pool2 <- pool(fit2)
pool3 <- pool(fit3)
pool4 <- pool(fit4)
pool5p <- pool(fit5p)
pool5n <- pool(fit5n)
```

Results
```{r Results}
summary(pool1)
summary(pool2)
summary(pool3)
summary(pool4)
summary(pool5n)
summary(pool5p)
```

Percent Variance Explained
```{r Percent Variance Explained}
pool.r.squared(fit1, adjusted=T)
pool.r.squared(fit2, adjusted=T)
pool.r.squared(fit3, adjusted=T)
pool.r.squared(fit4, adjusted=T)
pool.r.squared(fit5p, adjusted=T)
pool.r.squared(fit5n, adjusted=T)
```

